---
title: "TAR Template"
execute:
  echo: false
  include: false
  message: false
  warning: false
format: html
editor: visual
---

```{r}
#| label: setup
library(tidyverse)
library(dataRetrieval)

```




# Introduction – Atlas of Tribal Water Resources

Add information here about all of the water resources. This would be a great place to include maps, either interactive or static. Perhaps include the water quality standards associated with each site/reach/assessment unit. Maybe include a list of USGS stream gages and associated data in this section?

# Water quality monitoring program and assessment methods: Introduction-Monitoring Program Overview

Add information here about where and what you monitored, methods used and possibly in-line code that describes number of sites monitored during the time period, minimum and maximum dates, etc.

```{r}
#| label: USGSgagedata

#THIS IS FOR WEST ENFIELD GAGE STATION IN MAINE - CHANGE TO YOURS
siteNo <- "01034500"  #FIND YOUR GAGE AND CHANGE THE NUMBER

# this pcode is for discharge in cfs
#For a full list of pCodes see #https://help.waterdata.usgs.gov/code/parameter_cd_query?fmt=rdb&inline=true&group_cd=%
pCode <- "00060"

#CHANGE DATES YOU WANT TO PLOT
start.date <- "2023-10-01"
end.date <- "2024-09-30"

cfs <- readNWISuv(siteNumbers = siteNo,
                          parameterCd = pCode,
                          startDate = start.date,
                          endDate = end.date)

#test <- readNWISuv(siteNumbers = siteNo,parameterCd = pCode)

cfs <- renameNWISColumns(cfs)

parameterInfo <- attr(cfs, "variableInfo")
siteInfo <- attr(cfs, "siteInfo")

```



# Water quality monitoring program and assessment methods: Data Analysis Results

Summaries of results (including basic stats?) and whether sites/reaches/assessment units are meeting their water quality standards.

```{r}
#| label: cfsplot

Qplots <- ggplot(data = cfs, aes(dateTime, Flow_Inst)) +
  geom_line()+
  labs(title = paste0("USGS Flow Measurements on the ",siteInfo$station_nm), 
       x = "Date", 
       y = parameterInfo$variableDescription, 
       color = "Flow Measurement") +
  theme(legend.position = "bottom",
          legend.box = "vertical")
Qplots
```


# Water quality monitoring program and assessment methods: Discussion of issues of tribal concern

Include information about sources of pollution, habitat loss, reasons for not meeting standards etc.
