---
title: "TAR Template"
format: html
editor: visual
---

# Introduction – Atlas of Tribal Water Resources

Add information here about all of the water resources. This would be a great place to include maps, either interactive or static. Perhaps include the water quality standards associated with each site/reach/assessment unit. Maybe include a list of USGS stream gages and associated data in this section?

# Water quality monitoring program and assessment methods: Introduction-Monitoring Program Overview

Add information here about where and what you monitored, methods used and possibly in-line code that describes number of sites monitored during the time period, minimum and maximum dates, etc.

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

# Water quality monitoring program and assessment methods: Data Analysis Results

Summaries of results (including basic stats?) and whether sites/reaches/assessment units are meeting their water quality standards.

# Water quality monitoring program and assessment methods: Discussion of issues of tribal concern

Include information about sources of pollution, habitat loss, reasons for not meeting standards etc.
